\chapter{Advancements in MOE using ML and DL Approaches}
\label{chap:prev_works_moe_ml_dl}

\section{Introduction}
\gls{moe} serves as a cornerstone in applications like \gls{doa} estimation. This chapter offers a dual perspective:
an overarching view of machine learning and \gls{dnn} techniques in \gls{moe}, and a deep dive into the ChainNet
approach, a paradigm-shifting methodology in the field~\cite{barthelme2022chainnet}.

\section{Machine Learning and DNNs in MOE}

\subsection{The Rise of Neural Networks}
\gls{dnn}, particularly neural networks, have revolutionized \gls{moe} by capturing complex data relationships.
These networks have demonstrated superior performance, especially in low \gls{snr} conditions~\cite{barthelme2020}.

\subsection{Hybrid Methodologies}
Innovative works have merged neural networks with classical algorithms, achieving enhanced performance. For example,
neural network-based initialization coupled with model-based gradient steps has yielded competitive \gls{doa}
estimates~\cite{bialer2019performanceCHECK}.

\subsection{Adaptive Learning}
Online training mechanisms enable neural networks to adapt to real-world imperfections in antenna arrays, thereby
potentially obviating the need for manual calibration~\cite{barthelme2020}.

\section{The ChainNet Paradigm}

\subsection{Theoretical Underpinnings}
ChainNet approximates the Maximum A Posteriori (MAP) estimator through a multi-stage classification chain. Each stage
refines the \gls{doa} estimates, leveraging prior information from preceding stages.

\subsection{Benchmarking Performance}
ChainNet has been pitted against other machine learning-based methods such as SPICE + ML, \gls{music} + ML, and MCENet
+ ML, consistently outperforming them in terms of \gls{rmspe} across varying \gls{snr}s.

\subsection{Strengths and Weaknesses}
ChainNet excels in robustness and accuracy. However, its performance may wane when dealing with correlated sources.

% \section{Comparative Metrics}
% \begin{table}[h]
%     \centering
%     \begin{tabular}{c c c}
%         \toprule
%         Method         & Overall Accuracy & \gls{rmspe}    \\
%         \midrule
%         Neural Network & 97.25\%          & [Insert Value] \\
%         \midrule
%         ChainNet       & [Insert Value]   & [Insert Value] \\
%         \bottomrule
%     \end{tabular}
%     \caption{Comparative Metrics of \gls{moe} Methods}
% \end{table}

\section{Conclusion and Future Directions}
Machine learning, with neural networks and specialized frameworks like ChainNet at the forefront, is poised to redefine \gls{moe}. Future research avenues include architectural optimization, methodological diversification, and robustness assessments.
