\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\markright{}

I am deeply grateful to my thesis advisors, Dr.\ Karin Hedman at \textsc{Rohde \& Schwarz} and Prof.\ Dr.\ Arne Striegler
at \textsc{Munich University of Applied Sciences}. Their expertise, understanding, and patience have greatly enriched my
graduate experience. I am particularly appreciative of Dr.\ Hedman's personalized guidance and patience, which were
invaluable especially when my enthusiasm led to fervent discussions and explorations of alternative frameworks.

Furthermore, I would like to express my gratitude to Christoph Mayer for his enlightening Master's thesis and his
permission to use some of his exquisite illustrations. His work has been a source of inspiration and has notably
enriched the visual appeal of my thesis.

My sincere thanks go to the \textsc{PyTorch Lightning} community for developing a framework that alleviated the need to
deal with much of the boilerplate code, enabling me to focus on the essential aspects of developing deep learning
solutions. This thesis has undoubtedly benefited from the streamlined and efficient workflow that Python Lightning
facilitates.
My appreciation extends to both \textsc{Optuna} for their user-friendly framework for hyperparameter optimization,
which streamlined my experimentation process, and to the \textsc{Seaborn} library for its ability to create
sophisticated, informative statistical plots that enhanced the analytical depth of my research.

Lastly, I am grateful to the \LaTeX{} community. Utilizing \LaTeX{} for writing this thesis has been a pleasurable
experience, particularly when compared to the alternatives.

My journey through this thesis has been an amalgamation of support, guidance, and innovative tools, each contributing
uniquely to its completion. Though not always easy, this path has been incredibly enriching and formative, and I am
indebted to all who have been part of this enlightening experience.
